\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{datetime}

\input{glyphtounicode}

\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

\hypersetup{pdfborder = 0 0 0}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-0.15in}}{0em}{}[\color{black}\vspace{-8pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1\vspace{-2pt}}}
}

\newcommand{\resumeStint}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{@{}l@{\extracolsep{\fill}}r}
    \textbf{\small #1} & {\small #2}
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubstint}[2]{
  \vspace{-16pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{@{}l@{\extracolsep{\fill}}r}
    {\textit{\small#1}}&{\textit{\small#2}}
  \end{tabular*}%\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

%\setlength{\footskip}{4.08003pt}

\begin{document}

  %\pagestyle{fancy}
  %\fancyfoot{}
  %\fancyfoot[RE]{
  %  \color[rgb]{0.8,0.8,0.8}
  %  {\tiny\item Last updated: \monthyeardate\today}
  %}

  \vspace*{0.25in}

  % Header -----------------------------------------------------------------------------------------

  \begin{center}
    \textbf{\Huge\scshape Vishal Srivastava}\\
    \vspace{8pt}\small
    \faIcon{code}\href{https://svishal-aero.github.io}{
      svishal-aero.github.io
    }${ }{ }\bullet{ }{ }$
    \faIcon{linkedin}\href{https://linkedin.com/in/svishal-aero/}{
      svishal-aero
    }${ }{ }\bullet{ }{ }$
    \faIcon{envelope}\href{mailto:svishal.aero@gmail.com}{
      svishal.aero@gmail.com
    }${ }{ }\bullet{ }{ }$
    \faIcon{phone}+1$ $(734)$ $239-1484
  \end{center}

  % Education --------------------------------------------------------------------------------------

  \section{Education}
  \resumeSubHeadingListStart
    \resumeStint
    {University of Michigan, Ann Arbor}{May 2022}
    \resumeSubstint
    {Ph.D. (Aerospace Engineering, Advisor: Prof. Karthik Duraisamy)}{GPA: 4.0/4.0}
    \vspace{3pt}
    \resumeStint
    {Indian Institute of Technology, Kanpur}{May 2016}
    \resumeSubstint
    {B.Tech. (Aerospace Engineering)}{CPI: 9.5/10.0}
  \resumeSubHeadingListEnd

  % Awards -----------------------------------------------------------------------------------------

  \section{Awards}
  \resumeSubHeadingListStart
    \resumeItem{
      \textbf{General Proficiency Medal} (Convocation, 2016 - IIT Kanpur) for ranking first in
      Aerospace Engineering
    }
  \resumeSubHeadingListEnd

  % Research Interests -----------------------------------------------------------------------------

  \section{Research Interests}
  {
    \small
    \begin{center}
      \begin{tabular*}{0.97\textwidth}[t]{@{\vspace{3pt}}l@{\extracolsep{\fill}}l@{\extracolsep{\fill}}l}
      $\bullet$ Computational Aerodynamics & $\bullet$ Data-driven modeling & $\bullet$ Multidisciplinary Design \& Optimization\\
      $\bullet$ Scientific Machine Learning  & $\bullet$ Numerical Methods & $\bullet$ Reduced-order/Surrogate modeling
    \end{tabular*}
    \end{center}
  }

  % Experience -------------------------------------------------------------------------------------

  \section{Experience}
  \resumeSubHeadingListStart
    \resumeStint
    {Analytical Mechanics Associates}{Hampton VA, USA}
    \resumeSubstint
    {Aerospace Engineer, Senior (Postdoctoral Researcher at NASA Langley)}{Jan 2024 -- Present}
    \vspace{7pt}
    \resumeSubstint
    {Engineer, Staff (Postdoctoral Researcher at NASA Langley)}{Jun 2023 -- Dec 2023}
    \vspace{3pt}
    \resumeStint
    {National Institute of Aerospace}{Hampton VA, USA}
    \resumeSubstint
    {Research Engineer I (Postdoctoral Researcher at NASA Langley)}{Jul 2022 -- May 2023}
    \vspace{3pt}
    \resumeStint
    {University of Michigan, Ann Arbor}{Ann Arbor MI, USA}
    \resumeSubstint
    {Postdoctoral Research Scholar (at Prof. Karthik Duraisamy's group)}{Jun 2022 -- Jul 2022}
  \resumeSubHeadingListEnd

  % Publications -----------------------------------------------------------------------------------

  \section{Journal Publications}
  {
    \small
    \begin{enumerate}
      \item
      Srivastava, V., Sulzer, V., Mohtat, P., Siegel, J. B., \& Duraisamy, K. (2023).%
      \textbf{
        A non-intrusive approach for physics-constrained learning with application to fuel cell
        modeling.%
      }\textit{
        Computational Mechanics, 72(2), 411-430.
      }

      \item
      Srivastava, V., \& Duraisamy, K. (2023).%
      \textbf{
        Generalizable physics-constrained modeling using learning and inference assisted by
        feature-space engineering.%
      }\textit{
        Physical Review Fluids, 6(12), 124602.
      }
    \end{enumerate}
  }

  \section{Conference Proceedings}
  {
    \small
    \begin{enumerate}
      \item
      Srivastava, V., Rumsey, C. L., Coleman, G. N., \& Wang, L. (2024).%
      \textbf{
        On generalizably improving RANS predictions of flow separation and reattachment.
      }In\textit{
        AIAA SCITECH 2024 Forum (p. 2520).
      }

      \item
      Hildebrand, N., Srivastava, V., Zaki, T. A., \& Choudhari, M. M. (2023, September).%
      \textbf{
        DeepONet-Assisted Optimization of Surface Topography for Transition Delay in a Mach 4.5
        Boundary Layer.
      }In\textit{
        14th International ERCOFTAC Symposium on Engineering Turbulence Modelling and
        Measurements (ETMM14) (No. 20230001917).
      }

      \item
      Hildebrand, N., Venkatachari, B. S., Srivastava, V., \& Choudhari, M. M. (2023, September).%
      \textbf{
        Recent Progress on RANS-Based Transition Model Verification.
      }In\textit{
        14th International ERCOFTAC Symposium on Engineering Turbulence Modelling 
        and Measurements (ETMM14).
      }

      \item
      Srivastava, V., \& Duraisamy, K. (2022).%
      \textbf{
        Towards a generalizable data-driven approach to predict separation-induced transition.
      }In\textit{
        12th International Symposium on Turbulence and Shear Flow Phenomena (TSFP12).
      }

      \item
      Srivastava, V., \& Duraisamy, K. (2018).%
      \textbf{
        Aerodynamic design of aircraft engine nozzles with consideration of model-form uncertainties.
      }In\textit{
        2018 AIAA Non-Deterministic Approaches Conference (p. 2175).
      }
    \end{enumerate}
  }

  \newpage

  % Extras -----------------------------------------------------------------------------------------

  \vspace*{0.25in}
  \section{Book Chapters}
  {
    \small
    \begin{enumerate}
      \item
      Duraisamy, K. \& Srivastava, V. (2025).%
      \textbf{
        Machine learning augmented modeling of turbulence.
      }In\textit{
        Data Driven Analysis and Modeling of Turbulent Flows (pp. 311-354). Academic Press.
      }
    \end{enumerate}
  }

  \section{Technical Reports}
  {
    \small
    \begin{enumerate}
      \item
      Srivastava, V., Rumsey, C. L., Coleman, G. N., \& Wang, L. (2024).%
      \textbf{
        Augmenting RANS Turbulence Models Guided by Field Inversion and Machine Learning.%
      }\textit{
        (No. NASA/TM-20240012512).
      }
    \end{enumerate}
  }

  \section{Invited Talks/Lectures}
  {
    \small
    \begin{enumerate}
      \item
      Srivastava, V., Rumsey, C. L., Coleman, G. N., \& Wang, L. (2025).%
      \textbf{
        Data-driven Improvements in RANS Predictions for Reattachment of Separated Flows.%
      }\textit{
        137th NIA CFD Seminar. National Institute of Aerospace.
      }

      \item
      Srivastava, V. (2024).%
      \textbf{
        An Introduction to Machine Learning for Turbulence Modeling.%
      }\textit{
        MAE298: Fundamentals of Turbulence Modeling (Course Instructor: Dr. Camli Badrya), UC Davis
      }

      \item
      Srivastava, V., \& Duraisamy, K. (2019).%
      \textbf{
        Developing Data-Augmented Turbulence Models using Field Inversion and Machine Learning.%
      }\textit{
        120th NIA CFD Seminar. National Institute of Aerospace.
      }
    \end{enumerate}
  }

  \section{Skills}
  {
    \small
    \begin{center}
    \begin{tabular*}{0.97\textwidth}[t]{@{\vspace{3pt}}l@{\extracolsep{10pt}}l}
      \textbf{Programming Languages:} & C/C++, Python, FORTRAN, Julia, MATLAB \\
      \textbf{Machine Learning Packages:} & PyTorch, Keras (Tensorflow) \\
      \textbf{Scientific Computing Libraries:} & BLAS, LAPACK, PETSc, (Par)METIS, ADOL-C, CoDiPack \\
      \textbf{Parallel/Hybrid Computing Paradigms:} & OpenMP, MPI, CUDA, Kokkos \\
    \end{tabular*}
    \end{center}
  }

\end{document}
